A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-14 paper.tex

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{AES-NI}
    \caption{AES256 Encryption/Decryption Performance Numbers}
    \label{fig:AES-NI}
\end{figure}

The E2EE protocol presented in this paper combines a series of different cryptographic procedures. Each of them can be chosen on the basis of the working hardware and scenario by developers. On some certain devices, hardware acceleration would be supported. With hardware acceleration, the elapsed time could be dropped a step more. For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Fig.~\ref{fig:AES-NI} shows the performance of Encryption/Decryption of AES256 with and without hardware acceleration.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3in]{mam_vs_e2ee}
    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
    \label{fig:mam_vs_e2ee}
\end{figure}

It the Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data. Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range. The bump of MAM performance around 750 bytes proves this point. Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.

>>>>

\begin{table}[htbp]
	\caption{AES256 Encryption Performance Numbers}
	\label{tab:AES_NI}
	\begin{center}
        \begin{tabular}{ |c||c|c|c|  }
            %\hline
            %\multicolumn{4}{|c|}{} \\
            \hline
            Size& \makecell{NON AES-NI \\ (msecs)} & \makecell{AES-NI \\ (msecs)} & \makecell{Encryption \\ Acceleration (\%)} \\
            \hline
            50 MB  & 1026  & 563   & 45.13 \\
            100 MB & 2036  & 1297  & 36.30 \\
            200 MB & 4282  & 2984  & 30.31 \\
            512 MB & 10754 & 6401  & 40.48 \\
            1 GB   & 23976 & 15721 & 34.43 \\
            \hline
        \end{tabular}
    \end{center}
\end{table}

The E2EE protocol presented in this paper combines a series of different cryptographic procedures. Each of them can be chosen on the basis of the working hardware and scenario by developers. On some certain devices, hardware acceleration would be supported. With hardware acceleration, the elapsed time could be dropped a step more. For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.

@@

\begin{table}[htbp]
	\caption{Compare the performance between MAM and E2EE on Raspberry Pi}
    \label{tab:mam_vs_e2ee}
    \centering
        \begin{tabular}{|c||c|c|}
        \hline
            \textbf{size (bytes)} & \textbf{MAM(ms)} & \textbf{E2EE(ms)} \\
            \hline
            100 & 20.28 & 9.21 \\ 
            500 &  26.92 & 9.27 \\ 
            900 & 32.02 &  9.35  \\ 
            1300 & 36.67 & 9.41 \\ 
            1700 & 40.55 & 9.54 \\
            \hline
        \end{tabular}
\end{table}

It the Table~\ref{tab:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data.

\begin{gather}
    \label{eq:lin_mam_e2ee}
    y=0.0126 x+19.979 \\
    y=0.0002 x+9.174
\end{gather}

The equations in Eq.~\ref{eq:lin_mam_e2ee} are the linear equation for the experiment data of MAM and E2EE respectively. Apparently, the slope of the result of MAM is much greater than the result of E2EE. The small slope of E2EE ensures E2EE can consistently perform in an acceptable time range.

\subsubsection{Time Complexity}
With given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length. HMAC and AES-CBC are the procedures that cost most of the elapsed time. Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too. Therefore, the E2EE protocol framework takes only linear time versus arbitrary string length. Applying mature cryptographic functions (e.g. SHA-256, AES-CBC, etc), ensures gentle slope as Eq.~\ref{eq:lin_e2ee} shows.
